### 2020-02-03 paper2/paper.tex
submit for internal rev.

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Flow-assisted droplet assembly in a 3D microfluidic channel] % Short title used in headlines (optional)
{%
  Flow-assisted droplet assembly in a 3D microfluidic channel% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Flow-assisted droplet assembly in a 3D microfluidic channel} % Title for toc
%
\paperauthor[Ge, Tammisola, Brandt] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge, Outi Tammisola, Luca Brandt%
}%
%
\listpaperauthor{Z. Ge, O. Tammisola, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Soft Matter.] % Short publish info used in List Of Papers
{%
	Soft Matter%
}%
%
\papervolume{15}%
%
\papernumber{}%
%
\paperpages{3451--3460}%
%
\paperyear{2019}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
In this paper, we perform a series of simulations, using methods developed in \emph{Paper 1},
to examine the droplet interaction in increasingly realistic conditions, mimicking a microfluidic experiment.
The main objective is to elucidate the physical mechanism that leads to the experimentally observed droplet clustering,
which had been explained by a dipolar interaction theory.
Contrary to previous belief, we find that dipolar interactions alone cannot account for the fast droplet dynamics;
a number of 3D effects must be included to faithfully reproduce the observation.
This conclusion is supported by theoretical derivations of particle interactions in the Stokes flow (\emph{Papers 3 \& 4}),
implying that designing optimal microfluidic channels to directly produce large droplet crystals remains difficult in practice.
}%
%
\graphicspath{{paper2/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

>>>>

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Flow-assisted droplet assembly in a 3D microfluidic channel] % Short title used in headlines (optional)
{%
  Flow-assisted droplet assembly in a 3D microfluidic channel% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Flow-assisted droplet assembly in a 3D microfluidic channel} % Title for toc
%
\paperauthor[Ge, Tammisola, Brandt] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge, Outi Tammisola, Luca Brandt%
}%
%
\listpaperauthor{Z. Ge, O. Tammisola, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Soft Matter.] % Short publish info used in List Of Papers
{%
	Soft Matter%
}%
%
\papervolume{15}%
%
\papernumber{}%
%
\paperpages{3451--3460}%
%
\paperyear{2019}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
In this paper, we perform a series of simulations using methods developed in \emph{Paper 1}
to examine the droplet interactions in increasingly realistic conditions, mimicking a microfluidic experiment.
The main objective is to elucidate the physical mechanism that leads to the experimentally observed droplet clustering,
which had been explained by a dipolar interaction theory.
Contrary to previous belief, we find that dipolar interactions alone cannot account for the fast droplet rearrangement;
a number of 3D effects, which are hard to model at once, must be included to faithfully reproduce the observation.
This conclusion is supported by theoretical derivations of particle interactions in Stokes flow (\emph{Papers 3 \& 4}),
suggesting that designing optimal microfluidic channels to directly produce large droplet crystals remains difficult in practice.
}%
%
\graphicspath{{paper2/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

### 2020-02-03 paper3/paper.tex
submit for internal rev.

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Integral representation of channel flow with interacting particles] % Short title used in healines (optional)
{%
 Integral representation of channel flow with interacting particles% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Integral representation of channel flow with interacting particles} % Title for toc
%
\paperauthor[Fouxon, Ge, Brandt, Leshansky] % Short authors used in headlines and List Of Papers
{%
  Itzhak Fouxon$^{1,2}$, Zhouyang Ge$^3$, Luca Brandt$^3$, \\Alexander Leshansky$^1$%
}%
%
\listpaperauthor{I. Fouxon, Z. Ge, L. Brandt, A. Leshansky}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Department of Chemical Engineering, Technion, Haifa 32000, Israel\\%
  $^2$ Department of Computational Science and Engineering, Yonsei University, \\Seoul 120-749, South Korea\\%
  $^3$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Phys.\ Rev.\ E.] % Short publish info used in List Of Papers
{%
	Physical Review E%
}%
%
\papervolume{96}%
%
\papernumber{063110}
%
\paperpages{}%
%
\paperyear{2017}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   \todo
}%
%
\graphicspath{{paper3/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

>>>>

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Integral representation of channel flow with interacting particles] % Short title used in healines (optional)
{%
 Integral representation of channel flow with interacting particles% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Integral representation of channel flow with interacting particles} % Title for toc
%
\paperauthor[Fouxon, Ge, Brandt, Leshansky] % Short authors used in headlines and List Of Papers
{%
  Itzhak Fouxon$^{1,2}$, Zhouyang Ge$^3$, Luca Brandt$^3$, \\Alexander Leshansky$^1$%
}%
%
\listpaperauthor{I. Fouxon, Z. Ge, L. Brandt, A. Leshansky}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Department of Chemical Engineering, Technion, Haifa 32000, Israel\\%
  $^2$ Department of Computational Science and Engineering, Yonsei University, \\Seoul 120-749, South Korea\\%
  $^3$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Phys.\ Rev.\ E.] % Short publish info used in List Of Papers
{%
	Physical Review E%
}%
%
\papervolume{96}%
%
\papernumber{063110}
%
\paperpages{}%
%
\paperyear{2017}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   In this first part of a two-part theoretical work on droplet interactions,
   we consider the far-field interaction of spherical droplets or particles traveling in the Poiseuille flow.
   A boundary integral representation of the disturbance flow is derived,
   showing that, to leading order, the flow is dipolar and proportional to a weighted integral of the stress and flow at the particle surface.
   We tabulate the dipole moment under various confinement and particle initial positions by directly simulating a rigid particle in fully-resolved channel flow,
   using a second-order accurate immersed boundary method.
   Analytically, we also introduce the equation of motion that describes hydrodynamic interactions and solve it in the cases of two and three particles. 
}%
%
\graphicspath{{paper3/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

### 2020-02-03 paper4/paper.tex
Paper 4 added.
submit for internal rev.

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Two spheres in wall-bounded shear flow] % Short title used in healines (optional)
{%
 The theory of hydrodynamic interaction of \\two spheres in wall-bounded shear flow% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{The theory of hydrodynamic interaction of two spheres in wall-bounded shear flow} % Title for toc
%
\paperauthor[Fouxon, Rubinstein, Ge, Brandt, Leshansky] % Short authors used in headlines and List Of Papers
{%
  Itzhak Fouxon$^{1,2}$, Boris Rubinstein$^3$, Zhouyang Ge$^4$, \\Luca Brandt$^4$, Alexander Leshansky$^1$%
}%
%
\listpaperauthor{I. Fouxon, B. Rubinstein, Z. Ge, L. Brandt, A. Leshansky}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Department of Chemical Engineering, Technion, Haifa 32000, Israel\\%
  $^2$ Department of Computational Science and Engineering, Yonsei University, \\Seoul 120-749, South Korea\\%
  $^3$ Stowers Institute for Medical Research, 1000 E 50th st., Kansas City, \\MO 64110, USA\\%
  $^4$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Under review for Phys.\ Rev.\ Fluids] % Short publish info used in List Of Papers
{%
	Under review for Physical Review Fluids%
}%
%
\papervolume{}%
%
\papernumber{}
%
\paperpages{}%
%
\paperyear{}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   \todo
}%
%
\graphicspath{{paper4/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

@@

%------------------------------------------------------------------------------
% Bibliography
%------------------------------------------------------------------------------
%
%\clearpage
\bibliographystyle{jfm}
\bibliography{thesis}
%
\IfFileExists{paper4/paper.bbl}{\input{paper4/paper.bbl}}{}

>>>>

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Two spheres in wall-bounded shear flow] % Short title used in healines (optional)
{%
 The theory of hydrodynamic interaction of \\two spheres in wall-bounded shear flow% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{The theory of hydrodynamic interaction of two spheres in wall-bounded shear flow} % Title for toc
%
\paperauthor[Fouxon, Rubinstein, Ge, Brandt, Leshansky] % Short authors used in headlines and List Of Papers
{%
  Itzhak Fouxon$^{1,2}$, Boris Rubinstein$^3$, Zhouyang Ge$^4$, \\Luca Brandt$^4$, Alexander Leshansky$^1$%
}%
%
\listpaperauthor{I. Fouxon, B. Rubinstein, Z. Ge, L. Brandt, A. Leshansky}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Department of Chemical Engineering, Technion, Haifa 32000, Israel\\%
  $^2$ Department of Computational Science and Engineering, Yonsei University, \\Seoul 120-749, South Korea\\%
  $^3$ Stowers Institute for Medical Research, 1000 E 50th st., Kansas City, \\MO 64110, USA\\%
  $^4$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Under review for Phys.\ Rev.\ Fluids] % Short publish info used in List Of Papers
{%
	Under review for Physical Review Fluids%
}%
%
\papervolume{}%
%
\papernumber{}
%
\paperpages{}%
%
\paperyear{}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   In the second part of the theoretical investigation on droplet interactions in shear flow,
   we revisit the classical work of \cite{batchelor_green_1972}, where two spherical particles interact hydrodynamically in a unbounded linear flow.
   Using the boundary integral formulation derived in \emph{Paper 3},
   we show that the inclusion of a distant wall results in qualitatively different particle trajectories, demonstrative of the wall's singular perturbation.
   Specifically, the distance at which the wall significantly alters the particles interaction scales as $z_0^{3/5}$,
   where $z_0$ is the initial distance between the particle and the wall.
   The phase portrait of the particle relative paths admits domains of closed (dancing) and open (swapping) trajectories,
   apart from those that also exist in unbounded shear flows.
   We postulate that the patterns are topologically stable and verified it by direct numerical simulations of the Navier-Stokes equations.
   Qualitatively, the distant wall is the third body that changes the global topology of the phase portrait of two-particle interaction.
}%
%
\graphicspath{{paper4/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

@@

%------------------------------------------------------------------------------
% Bibliography
%------------------------------------------------------------------------------
%
\clearpage
\bibliographystyle{jfm}
\bibliography{thesis}
%
\IfFileExists{paper4/paper.bbl}{\input{paper4/paper.bbl}}{}

### 2020-02-03 paper5/paper.tex
submit for internal rev.

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Droplets in homogeneous shear turbulence] % Short title used in headlines (optional)
{%
  Droplets in homogeneous shear turbulence% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Droplets in homogeneous shear turbulence} % Title for toc
%
\paperauthor[Rosti, Ge, Jain, Dodd, Brandt] % Short authors used in headlines and List Of Papers
{%
  Marco E. Rosti$^1$, Zhouyang Ge$^1$, Suhas S. Jain$^2$, \\Michael S. Dodd$^2$, Luca Brandt$^{1,3}$%
}%
%
\listpaperauthor{M.E. Rosti, Z. Ge, S.S. Jain, M.S. Dodd, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden\\%
  $^2$ Center for Turbulence Research, Stanford University, CA 94305, USA\\%
  $^3$ Department of Energy and Process Engineering, Norwegian University of Science and Technology (NTNU), NO 7491, Norway%
}%
%
\paperjournal[J. Fluid Mech.] % Short publish info used in List Of Papers
{%
	Journal of Fluid Mechanics%
}%
%
\papervolume{876}%
%
\papernumber{}%
%
\paperpages{962--984}%
%
\paperyear{2019}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   This paper reports a simulation study of liquid droplets immersed in another density- and viscosity-matched fluid (5\% volume fraction)
   in homogeneous shear turbulent flow at a shear Reynolds number equal to 15 200.
   Detailed fluid motions are visualised, showing intense deformation, breakup, and coalesence of the droplets as the flow evolves.
   We examine the flow and droplet statistics, including Taylor-microscale Reynolds numbers, turbulent kinetic energy budget, droplet size distributions, etc.,
   under various surface tensions and initial droplet diameters.
   The overall results suggest that the dispersed phase acts as a sink of the turbulent kinetic energy for the carrier fluid, and
   the maximal droplet sizes are predicted by the Hinze scaling despite of droplet coalescence and a mean shear.
}%
%
\graphicspath{{paper5/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

>>>>

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Droplets in homogeneous shear turbulence] % Short title used in headlines (optional)
{%
  Droplets in homogeneous shear turbulence% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Droplets in homogeneous shear turbulence} % Title for toc
%
\paperauthor[Rosti, Ge, Jain, Dodd, Brandt] % Short authors used in headlines and List Of Papers
{%
  Marco E. Rosti$^1$, Zhouyang Ge$^1$, Suhas S. Jain$^2$, \\Michael S. Dodd$^2$, Luca Brandt$^{1,3}$%
}%
%
\listpaperauthor{M.E. Rosti, Z. Ge, S.S. Jain, M.S. Dodd, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden\\%
  $^2$ Center for Turbulence Research, Stanford University, CA 94305, USA\\%
  $^3$ Department of Energy and Process Engineering, Norwegian University of Science and Technology (NTNU), NO 7491, Norway%
}%
%
\paperjournal[J. Fluid Mech.] % Short publish info used in List Of Papers
{%
	Journal of Fluid Mechanics%
}%
%
\papervolume{876}%
%
\papernumber{}%
%
\paperpages{962--984}%
%
\paperyear{2019}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   This paper reports a simulation study of liquid droplets immersed in a density- and viscosity-matched fluid (5\% volume fraction)
   in homogeneous shear turbulent flow at a shear Reynolds number equal to 15200.
   Detailed fluid motions are visualised, showing intense deformation, breakup and coalesence of the droplets as the flow evolves.
   We examine the flow and droplet statistics, including Taylor-microscale Reynolds numbers, turbulent kinetic energy budget, droplet size distributions, etc.,
   under various surface tensions and initial droplet diameters.
   The overall results suggest that the dispersed phase acts as a sink of the turbulent kinetic energy for the carrier fluid, and
   the maximal droplet sizes are predicted by the Hinze scaling despite of droplet coalescence and a mean shear.
}%
%
\graphicspath{{paper5/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

### 2020-02-03 paper6/paper.tex
submit for internal rev.

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Effective slip over partially filled microcavities] % Short title used in headlines (optional)
{%
  Effective slip over partially filled microcavities and its possible failure% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Effective slip over partially filled microcavities and its possible failure} % Title for toc
%
\paperauthor[Ge, Holmgren, Kronbichler, Brandt, Kreiss] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge$^1$, Hanna Holmgren$^2$, Martin Kronbichler$^3$, \\Luca Brandt$^1,$, Gunilla Kreiss$^2$%
}%
%
\listpaperauthor{Z. Ge, H. Holmgren, M. Kronbichler, L. Brandt, G. Kreiss}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden\\%
  $^2$ Division of Scientific Computing, Department of Information Technology, \\Uppsala University, Box 337, 751 05 Uppsala, Sweden\\%
  $^3$ Institute for Computational Mechanics, Technical University of Munich, Boltzmannstrasse 15, 85748 Garching b. München, Germany%
}%
%
\paperjournal[Phys. Rev. Fluids.] % Short publish info used in List Of Papers
{%
	Physical Review Fluids%
}%
%
\papervolume{3}%
%
\papernumber{054201}%
%
\paperpages{}%
%
\paperyear{2018}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   In this paper, we combine two separate simulation methods (phase field and level set methods) to numerically study
   the transverse flow over a 2D model liquid-infused surface (LIS).
   Computationally, we introduce and verifie a multiscale numerical framework for wetting modelling
   by locally solving the Cahn-Hilliard equations near the moving contact line within a larger Stokes system.
   Physically, we conduct a parametric study of the performance of the LIS, quantified by its effective slip length and potential drainage.
   Among the many parameters (the capillary number, viscosity ratio, contact angle, etc.) explored,
   we identify that filling fraction is the most sensitive parameter for the effective slip;
   the effects of other parameters are generally intertwined but weakened if the surface groove is not fully filled.
   Furthermore, we report a shear-driven failure mode associated with lubricant drainage,
   that is worse at higher lubricant viscosities if the lubricant is less viscous than the outer fluid,
   but disappears if the lubricant is more viscous.
   Overall, our study may serve as a conceptual guide for LIS design complementing experimental tests.
}%
%
\graphicspath{{paper6/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

>>>>

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Effective slip over partially filled microcavities] % Short title used in headlines (optional)
{%
  Effective slip over partially filled microcavities and its possible failure% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Effective slip over partially filled microcavities and its possible failure} % Title for toc
%
\paperauthor[Ge, Holmgren, Kronbichler, Brandt, Kreiss] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge$^1$, Hanna Holmgren$^2$, Martin Kronbichler$^3$, \\Luca Brandt$^1,$, Gunilla Kreiss$^2$%
}%
%
\listpaperauthor{Z. Ge, H. Holmgren, M. Kronbichler, L. Brandt, G. Kreiss}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden\\%
  $^2$ Division of Scientific Computing, Department of Information Technology, \\Uppsala University, Box 337, 751 05 Uppsala, Sweden\\%
  $^3$ Institute for Computational Mechanics, Technical University of Munich, Boltzmannstrasse 15, 85748 Garching b. München, Germany%
}%
%
\paperjournal[Phys. Rev. Fluids.] % Short publish info used in List Of Papers
{%
	Physical Review Fluids%
}%
%
\papervolume{3}%
%
\papernumber{054201}%
%
\paperpages{}%
%
\paperyear{2018}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   In this paper, we combine two separate simulation methods (phase field and level set methods) to numerically study
   the transverse flow over a 2D model liquid-infused surface (LIS).
   Computationally, we introduce and verify a multiscale numerical framework for wetting modelling,
   which solves the Cahn-Hilliard equations in a local region near the moving contact line within a larger Stokes system.
   Physically, we conduct a parametric study of the performance of the LIS, quantified by its effective slip length and potential drainage.
   Among the many parameters (the capillary number, viscosity ratio, contact angle, etc.) explored,
   we find that filling fraction is the most sensitive parameter for the effective slip;
   the effects of other parameters are generally intertwined, and are weakened if the surface groove is not fully filled.
   Furthermore, we report a shear-driven failure mode associated with the lubricant drainage.
   The failure is worse at higher lubricant viscosities, if the lubricant is less viscous than the outer fluid,
   but disappears if the lubricant is more viscous.
   Overall, we expect our study to serve as a conceptual guide for LIS design, and call for experimental tests to validate our findings.
}%
%
\graphicspath{{paper6/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

### 2020-02-03 paper7/paper.tex
summary rough
abstract (eng)
submit for internal rev.

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Note of DLCD for dense suspensions] % Short title used in healines (optional)
{%
 Implementation note on a minimal discrete-element lubrication/contact dynamics model for dense suspensions% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Implementation note on a minimal discrete-element lubrication/contact dynamics model for dense \\suspensions} % Title for toc
%
\paperauthor[Ge \& Brandt] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge \& Luca Brandt%
}%
%
\listpaperauthor{Z. Ge, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Technical Report] % Short publish info used in List Of Papers
{%
	Technical Report%
}%
%
\papervolume{}%
%
\papernumber{}
%
\paperpages{}%
%
\paperyear{}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   This report documents the implementation detail of a minimal discrete-element lubrication/contact dynamics (DLCD) model intended for simulation of dense particle suspensions in shear flows. The method is meshless, explicit, and solves directly the particle dynamics in the overdamped limit by balancing conservative and dissipative interactions at the pair level. Potential limitations include omissions of fluid/particle inertia and long-range hydrodynamic interactions. The implementation has been tested for $200\sim 500$ particles under volume fractions from 40\% to 64\%, showing jamming transition, continuous and discontinuous shear thickening that are in excellent agreement with literature results.
}%
%
\graphicspath{{paper7/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

>>>>

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Note of DLCD for dense suspensions] % Short title used in healines (optional)
{%
 Implementation note on a minimal discrete-\\element lubrication/contact dynamics model \\for dense suspensions% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Implementation note on a minimal discrete-element lubrication/contact dynamics model for dense \\suspensions} % Title for toc
%
\paperauthor[Ge \& Brandt] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge \& Luca Brandt%
}%
%
\listpaperauthor{Z. Ge, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  Linn\'e FLOW Centre and SeRC, Department of Engineering Mechanics,\\
  KTH Royal Institute of Technology, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Technical Report] % Short publish info used in List Of Papers
{%
	Technical Report%
}%
%
\papervolume{}%
%
\papernumber{}
%
\paperpages{}%
%
\paperyear{2020}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   This report documents the implementation detail of a minimal discrete-element lubrication/contact dynamics (DLCD) model
   intended for simulation of dense particle suspensions in shear flows.
   The method is meshless, explicit and solves directly the particle dynamics in the overdamped limit
   by balancing conservative and dissipative interactions at the pair level.
   Potential limitations include omissions of fluid/particle inertia and long-range hydrodynamic interactions.
   The implementation has been tested for $200\sim 500$ particles under volume fractions from 40\% to 64\%,
   showing jamming transition, continuous and discontinuous shear thickening that are in excellent agreement with literature results.
}%
%
\graphicspath{{paper7/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}
